Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-19 paper/responseToReviewers.tex

\item \emph{The second paragraph of the abstract is vague.}

This paragraph has been reworded and worked into the rest of the abstract in a more fluid manner.

\item \emph{No novel technique is presented.}

Again, the hierarchical representation proposed is, to the best of our knowledge, novel and we provide adequate evidence, in our opinion, for its power in the proposed similarity retrieval task in the case of environmental audio data processing.

@@

\item \emph{The whole paper architecture is poor.}

We have reworked the paper as a whole, trying to clarify the overall message. In particular, we reorganized the paper towards a unique claim, that is supported by experimental evidence. the contribution now explicitly target the acoustic similarity retrieval task. Complementary experiments in the more widely used classification task are used to validate the first step of representation using the scattering transform.

@@

\section{Responses to Reviewer 2}

\begin{enumerate}

\item \emph{The late versus early integration of the features is well presented and evaluated. But a graphic representation of the whole process would arise the novelty of the model.}

We acknowledge that such a diagram would help the reader, we are facing page limit constraints due to the extensive experiments described in the paper.

@@

\item \emph{Setting of Q1 shall be motivated.}

This has been added to the text.

\item \emph{Reproducibility:  data sets are publicly available, the author do not mention if they plan to make their model available.}

Experiments have been performed in the Matlab environment using open source libraries an all the authors are committed to comply to the reproducible research statements. The replication code is now available in beta, and will be doubled checked very soon.

### 2016-12-19 paper/structureScene.tex
dot at the end of keywords
start improving the abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}

An important task in the emerging field of computational ecoacoustics is to determine the similarity of two audio scenes to be able to get a high level understanding of large amount of audio recordings coming from large deployment of acoustics sensors that are continuously recordings the sonic environment. A convenient method considers bag-of-frames models and other representations based on summary statistics. While these successfully characterize static scenes with little variability in sound content, they are unable to accurately differentiate scenes characterized by a few distinct sound events superimposed over a static background. To address this problem, we propose a two-scale representation, which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure. To motivate this, we validate the use of scattering transforms for supervised acoustic scene classification (ASC), illustrating its state-of-the-art performance compared to traditional feature transforms like mel-frequency cepstral coefficients (MFCCs). Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) task, where we again significantly outperform more traditional approaches based on summary statistics of MFCCs.

@@

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
acoustic scene classification, acoustic scene similarity retrieval, cluster models, wavelets, scattering, invariance
\end{IEEEkeywords}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The emerging field of computational ecoacoustics aims at retrieving high-level information from the continuous, environmental recordings of acoustic sensors.
In this context, a central task is to cluster auditory scenes by similarity.
A convenient method considers bag-of-frames models and other representations based on summary statistics.
While these successfully characterize static scenes with little variability in sound content, they are unable to accurately differentiate scenes characterized by a few distinct sound events superimposed over a static background.
To address this problem, we propose a two-scale representation, which describes a signal at a short scale using scattering transforms while relying on a cluster model to characterize its larger-scale structure.
To motivate this, we validate the use of scattering transforms for supervised acoustic scene classification (ASC), illustrating its state-of-the-art performance compared to traditional features, such as mel-frequency cepstral coefficients (MFCCs).
Furthermore, we illustrate the power of the full cluster-based representation by applying it to an acoustic scene similarity retrieval (ASSR) task, where we again significantly outperform more traditional approaches based on summary statistics of MFCCs.

@@

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
acoustic scene classification, acoustic scene similarity retrieval, cluster models, wavelets, scattering, invariance.
\end{IEEEkeywords}
